{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-09 Paper/main.tex
More corrections

	In reality, these calculations are often implemented using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation. For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} d_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} d_{k}^m \psi_{k}(s) + \delta_{\beta}^K(s)\right)} \mathrm{d}s \\
			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s \\
			& \quad + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^K(s) \mathrm{d}s + \int_{0}^{1} \delta_i^J(s) \delta_{\beta}^K(s) \mathrm{d}s
		\end{split}
	\end{equation}

@@

	This method of deriving or approximating the Eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda. The following considerations and results of the simulation study might therefore serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method.

@@

	this leads to a considerable simplification of Equation \ref{basis_exp_transf}.
	\begin{equation}\label{simplified_model_basis_equation}
		\begin{split}
			Y(\omega) &= \alpha + \sum_{j = 1}^{L} b_j \tilde{Z}_j(\omega) + \sum_{j = 1}^{L} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{L}(\omega)(s) \mathrm{d}s\\
			& \quad + \sum_{k = 1}^{L} a_k  \int_{0}^{1} \delta_{\beta}^{L}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) + \int_{0}^{1}  \delta_{\beta}^{L}(s) \delta_{X}^{L}(\omega)(s) \mathrm{d}s + \epsilon(\omega)\\
			& \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)
		\end{split}
	\end{equation}

>>>>

	In reality, these calculations are often implemented using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation. For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} d_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} d_{k}^m \psi_{k}(s) + \delta_{\nu, m}^K(s)\right)} \mathrm{d}s \\
			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s \\
			& \quad + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\nu, m}^K(s) \mathrm{d}s + \int_{0}^{1} \delta_i^J(s) \delta_{\nu, m}^K(s) \mathrm{d}s
		\end{split}
	\end{equation}

@@

	This method of deriving or approximating the Eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda. The following considerations and results of the simulation study might therefore serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method instead of using more conventional smoothing approaches.

@@

	this leads to a considerable simplification of Equation \ref{basis_exp_transf}.
	\begin{equation}\label{simplified_model_basis_equation}
		\begin{split}
			Y(\omega) &= \alpha + \sum_{j = 1}^{L} b_j \tilde{Z}_j(\omega) + \sum_{j = 1}^{L} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{L}(\omega)(s) \mathrm{d}s\\
			& \quad \quad + \sum_{k = 1}^{L} a_k  \int_{0}^{1} \delta_{\beta}^{L}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) + \int_{0}^{1}  \delta_{\beta}^{L}(s) \delta_{X}^{L}(\omega)(s) \mathrm{d}s + \epsilon(\omega)\\
			& \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)
		\end{split}
	\end{equation}
